Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-08-20 mu/article/article.tex
Checking with bms.

Graphene, an allotrope of carbon with hexagonal 2D lattice structure,
demonstrates properties such as fractional quantum Hall effect at room
temperature, excellent thermal transport properties, excellent
conductivity\cite{heerscheNat07} and strength \cite{geimNM07, reinaNL08,
novoselov2S07, balandinNL08}, being a perfect platform  for two-dimension (2D)
electronic systems; however, most electronic applications are disabled by the
absence of a semiconducting gap. Recent studies demonstrate that a narrow band
gap  can be opened in graphene by applying an electric field,\cite{zhangN09}
reducing the surface area,\cite{hanPRL07} or applying uniaxial
strain.\cite{niACSN08} Another possibility to open the gap is by doping; this
has been successfully achieved using nitrogen,\cite{weiNL2009} boron-
nitrogen,\cite{guoIJ11} silicon,\cite{colettiPRB10} noble-
metals,\cite{varykhalovPRB10} and hydrogen.\cite{eliasS09, guisingerNL09,
samarakoonACSN10} Depending on the percentage of hydrogenation and spatial
arrangements of the hydrogen-carbon bonds, hydrogenated graphene demonstrates
different structural configurations and a tunable electron gap, as it has been
proven in [1]. In this paper, we present two 50\% hydrogenated graphene
noncentrosymmetric structures, both presenting a discernible band gap. The
first one, labelled as the Up structure, also known as
graphone,\cite{gmitraPRL13} shown in Fig. \ref{fig:up-struc}. Graphone has
hydrogen atoms bonded to the carbon layer only on the upper side of the
structure, we consider here the magnetic isomer of graphone, with the so-called
“chair” structure. In contrast,  the Alt structure, shown in Fig. 
\ref{fig:alt-struc}, has hydrogen alternating on the upper and bottom sides of 
the carbonsheet.\cite{zapataPSB2016}

>>>>

Graphene, an allotrope of carbon with hexagonal 2D lattice structure,
demonstrates properties such as fractional quantum Hall effect at room
temperature, excellent thermal transport properties, excellent
conductivity\cite{heerscheNat07} and strength \cite{geimNM07, reinaNL08,
novoselov2S07, balandinNL08}, being a perfect platform  for two-dimension (2D)
electronic systems; however, most electronic applications are disabled by the
absence of a semiconducting gap. Recent studies demonstrate that a narrow band
gap  can be opened in graphene by applying an electric field,\cite{zhangN09}
reducing the surface area,\cite{hanPRL07} or applying uniaxial
strain.\cite{niACSN08} Another possibility to open the gap is by doping; this
has been successfully achieved using nitrogen,\cite{weiNL2009} boron-
nitrogen,\cite{guoIJ11} silicon,\cite{colettiPRB10} noble-
metals,\cite{varykhalovPRB10} and hydrogen.\cite{eliasS09, guisingerNL09,
samarakoonACSN10} Depending on the percentage of hydrogenation and spatial
arrangements of the hydrogen-carbon bonds, hydrogenated graphene demonstrates
different structural configurations and a tunable electron gap, as it has been
proven in \cite{shkrebtiiPSSC12}. In this paper, we present two 50\% hydrogenated graphene
noncentrosymmetric structures, both presenting a discernible band gap. The
first one, labelled as the Up structure, also known as
graphone,\cite{gmitraPRL13} shown in Fig. \ref{fig:up-struc}. Graphone has
hydrogen atoms bonded to the carbon layer only on the upper side of the
structure, we consider here the magnetic isomer of graphone, with the so-called
“chair” structure. In contrast,  the Alt structure, shown in Fig. 
\ref{fig:alt-struc}, has hydrogen alternating on the upper and bottom sides of 
the carbonsheet.\cite{zapataPSB2016}
